---
title: "here-package-demo"
author: "Ashirwad Barnwal"
date: "9/18/2021"
output: html_document
---

**Step 1**: Load the *here* package

```{r}
library(here)
```

Notice that when *here* package is loaded it instructs a user about the working directory.

**Step 2**: Construct file paths relative to project root in a more intuitive manner

```{r}
here("demo", "data", "mtcars.csv")
```

**Step 3**: Let's read a csv file

```{r}
# use relative path
read.csv("data/mtcars.csv")

# use path constructed via here::here
read.csv(here("demo", "data", "mtcars.csv"))
```

**Step 4**: Let's move this Rmarkdown file into a sub-folder of *demo* folder and import the *mtcars.csv* again

```{r}
# this will fail because relative path has changed
read.csv("data/mtcars.csv")

# we need to tweak the relative path for it work
read.csv("../data/mtcars.csv")

# this will work correctly since here::here constructs absolute paths
read.csv(here("demo", "data", "mtcars.csv"))
```

We can see that the paths constructed using *here::here* are more robust to file reorganizations.




