---
title: "fs-demo"
author: "Ashirwad Barnwal"
date: "9/18/2021"
output: html_document
---

Let's see a demo of differences between *fs* and base R functions.

**Step 1**: Load the *fs* package

```{r}
library(fs)
```

**Step 2**: Get the list of files in the current directory

```{r}
# fs package
dir_ls()

# base R
list.files()
```

Notice that the output of *dir_ls()* renders nicely and is color coded to visually distinguish files and directories.

**Step 3**: Get the list of directories in the current directory

```{r}
# fs package
dir_ls(type = "directory")

# base R (need a new function)
list.dirs(full.names = FALSE, recursive = FALSE)
```

Notice that to get just the list of directories we need to use a separate function in base R, but it can be accomplished using the same *dir_ls()* function by changing one of the arguments.

**Step 4**: Get the list of directories in the current directory (only recurse to a certain level)

```{r}
# fs package
dir_ls(recurse = 1, type = "directory")
dir_ls(recurse = 2, type = "directory")

# base R (no such option to recurse to a specific level, either it's recursive or non-recursive)
list.dirs(full.names = FALSE, recursive = FALSE)
list.dirs(full.names = FALSE, recursive = TRUE)
```






